Edge sign prediction in general graphs and Correlation Clustering

### 2017-09-10 troll/introduction.tex
add some applications in the troll intro

\section{Introduction}
% say that we are facing edge sign prediction from many viewpoints.
% say about trolls and trustworthy people in a social network
% say that we are using reductions to node classification (novelty)
% generative model
% novel and cool

Connections in social networks are mostly driven by the \emph{homophily} assumption: linked
individuals tend to be similar, sharing personality traits, attitudes, or interests. However,
homophily alone is clearly not sufficient to explain the variety of social links\Todo{link with
chapter 3}. In fact, sociologists have long studied networks, hereafter called \emph{signed} social
networks\Todo{DSSN?}, where also {\em negative} relationships ---like dissimilarity, disapproval or
distrust--- are explicitly displayed. The presence of negative relationships is also a feature of
many technology-mediated social networks. Known examples are \textsc{Ebay}, where users trust or
distrust agents in the network based on their personal interactions, \textsc{Slashdot}, where each
user can tag another user as friend or foe, and \textsc{Epinion}, where users can rate positively
or negatively not only products, but also other users. Even in social networks where connections
solely represent friendships, negative links can still emerge from the analysis of online debates
among users.

>>>>

As we saw in the introduction, many situations in various fields can be modeled by signed graphs.
One of the most natural usage of signed graphs, though, is the study of social networks. That is
indeed what first motivated their inception. Quite naturally, we thus begin our exploration of the
role of edges in complex networks by a binary classification problem in signed graphs. Namely, we
want to predict whether an observed interaction between two nodes is positive or negative and we
call this problem \esp{}.\footnote{This chapter is closely based on a paper written with several
co-authors~\autocite{trollSign17}.} To motivate this problem from a practical point of view, let us
first define precisely the type of social networks we consider. We call \emph{Directed Signed Social
Network} (DSSN) a directed graph whose nodes are either human beings (often called users if they are
the members of an online community) or artifacts directly created by individuals\footnote{This
semantic detail allows us to treat citation networks as social networks.}. Furthermore, a directed
edge from node $u$ to node $v$ denote an interaction initiated by the user $u$ and whose object is
user $v$. Such an interaction can be positive (to praise, to support, to trust, to befriend) or
negative (to criticize, to oppose, to distrust, to befoe).

Known examples are \textsc{Ebay}, where users trust or distrust agents in the network based on their
personal interactions, \textsc{Slashdot}, where each user can tag another user as friend or foe,
\textsc{BlaBlaCar}, a carpooling website where users can evaluate drivers and passengers as pleasant
travelers or not, and \textsc{Epinion}, where users can rate positively or negatively not only
products, but also other users. In such examples, the sign of the interaction is explicit. However,
there are other cases where such interactions are only displayed in their raw form and need further
processing to be given a sign. The typical situation where this happens is when interactions are
mediated through text, for instance in Twitter or in the comment section of some online content. It
is then possible to extract signs using sentiment analysis methods~\autocite{signedText12}.

Another distinction is that in most cases, only the owner of the network can observe its graph.
Think for instance of \textsc{YouTube}, where users can like or dislike the video of another user
but where only aggregate anonymous statistics are available publicly. The situation is similar on
the \textsc{Stack Overflow} community, where users can upvote or downvote answers according to their
perceived quality, but where only the total score are available.

\bigskip

With this definition of social networks, we now look at how the learning problem of \esp{} can be
used in real world applications. More precisely, we present four possible applications, and order
them by how severely negative interactions impact the well-being of users of the networks.
First, it could help improve the quality of link recommendation in solely positive networks. Such
networks indeed contain implicit negative links~\autocite{Yang2012}. By asking users to label a
small proportion of existing links as truly positive or actually negative, recommended links could
be discarded if they are predicted to be negative.
%
Second, this could be used to monitor news textual comments in a scalable fashion and thus ensure
that online debates remain courteous and constructive. For instance, \textcite{betterDebate14} show
that by visually reminding comment authors of the importance of respecting the plurality of
opinions, the quality of debates is improved (other references can be found
in~\autocite{journalism15}).
%
Third, like many other fields, human resource management is undergoing a transformation through the
increasing use of Machine Learning~\autocite{MLinHR16}. Among other tools, assessing personal
relationships between employees is crucial to maintain a productive work environment. Whereas this
can be done by invasive wearable sensors~\autocite{WearableBehavior09}, our methods could predict
which employees would form the tighter teams from a small amount of labeled data.
%
Fourth, and most critical, predicting the sign of interactions could be a tool to detect users with
a high proportion of negative interactions. Indeed, because people tend to be less inhibited in
their online interactions~\cite{Suler04}, some users may join an online community with the main goal
to disrupt it, by engaging into anti-social behavior and creating conflictual relationships with
other members. This kind of attitude expressed publicly on social media leads to the following
definition of \emph{trolls}: \enquote{users whose real intentions are to cause disruption and/or to
trigger or exacerbate conflict for the purposes of their own amusement}~\autocite{Hardaker10}.
\Textcite{Shachaf10} elaborate on their motives, adding that boredom, attention seeking, and
revenge motivate trolls; they find pleasure from causing damage to other people or to the community
as a whole. An extreme form of trolling is bullying (\ie{} the behavior of someone intentionally and
repeatedly harming a victim that is unable to defend himself or herself) and just like anything
else, it has an online version called cyber bullying~\autocite{cyberbullying13}. Such behavior is
rather widespread, one study revealing that 72\% of \np{1454} surveyed teenagers reported at least
one occurrence of cyberbullying, most of them through instant messaging~\autocite{Juvonen08}. While
we have not conducted experimental study on this topic, we believe that being able to predict such
harmful interactions would be beneficial for the majority of users.
